\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead[L]{Pearson Edexcel IAL Statistics 2}
\fancyhead[R]{Chapter 1: Binomial Distributions}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}
\begin{document}
\centerline{\Large\textbf{Classwork Challenge: Binomial Probabilities (Set 3)}}
\centerline{\textbf{Pearson Edexcel International A Level Statistics 2}}

\vspace{0.5cm}
\textbf{Instructions:} Answer all questions, showing clear working where appropriate. You may use a calculator. These questions are based on calculating specific probabilities within a binomial distribution.
\vspace{0.5cm}

\begin{enumerate}
    \item \textbf{Direct Application of the Binomial Probability Formula}
    A random variable $X$ follows a binomial distribution $X \sim B(15, 0.2)$.
    \begin{enumerate}
        \item Write down the binomial probability formula for $P(X=x)$.
        \item Using the formula, calculate $P(X=3)$, giving your answer to 4 decimal places.
    \end{enumerate}

    \item \textbf{Real-World Scenario: Quality Control}
    In a manufacturing process, it is known that $8\%$ of items produced are defective. A quality control inspector randomly selects a sample of 12 items.
    \begin{enumerate}
        \item Define a suitable binomial distribution to model the number of defective items in the sample, stating its parameters.
        \item Calculate the probability that exactly 1 item in the sample is defective, giving your answer to 4 decimal places.
    \end{enumerate}

    \item \textbf{Real-World Scenario: Customer Preferences}
    A survey indicates that $60\%$ of customers prefer product A over product B. If 10 customers are randomly selected, let $C$ be the number of customers who prefer product A.
    \begin{enumerate}
        \item Find the probability that exactly 7 of the selected customers prefer product A.
        \item Find the probability that exactly 3 of the selected customers do *not* prefer product A.
    \end{enumerate}

    \item \textbf{Probability for a Specific Number of Successes and Failures}
    An unbiased coin is tossed 8 times. Let $H$ be the number of heads obtained.
    \begin{enumerate}
        \item Calculate the probability of obtaining exactly 5 heads.
        \item Calculate the probability of obtaining exactly 3 tails.
    \end{enumerate}

    \item \textbf{Binomial Probability with Different Parameters}
    A student is taking a multiple-choice quiz with 10 questions. Each question has 5 possible answers, only one of which is correct. The student answers all questions randomly.
    \begin{enumerate}
        \item What is the probability that the student answers exactly 4 questions correctly? Give your answer to 4 decimal places.
        \item What is the probability that the student answers exactly 6 questions incorrectly? Give your answer to 4 decimal places.
    \end{enumerate}
\end{enumerate}
\end{document}
